Questioning how Researchers Present Intrusion Detection Systems

### 2014-09-22 docs/questioning.tex
some additions - changes

\title{Questioning how Researchers Develop and Present Intrusion Detection Systems}

@@

    & \multicolumn{2}{|c|}{Requirements}

@@

	& \bf{Computational Overhead}\tnote{4} & \\

@@

    &   {\it {\sc didafit}}~\cite{LLW02} & 85 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\bf ?} & {\sc sql} injection \\
	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & 118,66,376 & (1470,{\sc nq},0,0)\_a & {\bf ?} & {\sc sql} injection \\ 

@@

	& 	{\it {\sc sm}ask}~\cite{JB07} & 27 & (5,{\sc nq},{\sc nq},{\sc nq})\_r  & {\bf ?} & {\sc sql} injection, {\sc xss} \\
	& 	{\it {\sc xssds}}~\cite{JEP08} & 64 & ({\sc nq},{\sc nq},{\sc nq},0)\_r & {\bf ?} &  {\sc xss} \\

@@

       \item[1] {\it Flexibility} indicates if the approach can be adjusted
	in order to detect different {\sc cia} categories.
       \item[4] {\it User Experience} is affected if the mechanism suffers
	from runtime overhead.

@@

{\sc na} means that a requirement is not even mentioned in the paper.
{\sc nq} indicates that a requirement is mentioned in the publication
but it is not quantified.

>>>>

\title{Questioning how Researchers Present Intrusion Detection Systems}

@@

    & \multicolumn{2}{|c|}{Requirements\tnote{1}}

@@

	& \bf{Computational Overhead} & \\

@@

    &   {\it {\sc didafit}}~\cite{LLW02} & 85 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} & {\sc sql} injection \\
	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & 118,66,376 & (1470,{\sc nq},0,0)\_a & {\sc nq} & {\sc sql} injection \\ 

@@

	& 	{\it {\sc sm}ask}~\cite{JB07} & 27 & (5,{\sc nq},{\sc nq},{\sc nq})\_r  & {\sc na} & {\sc sql} injection, {\sc xss} \\
	& 	{\it {\sc xssds}}~\cite{JEP08} & 64 & ({\sc nq},{\sc nq},{\sc nq},0)\_r & {\sc nq} &  {\sc xss} \\

@@

       \item[1] {\sc na} (Not Available) means that a requirement is not even mentioned in the paper.
	{\sc nq} (Not Quantified) indicates that a requirement is mentioned in the publication
	but it is not quantified.

@@
